Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-22 doc/JFLA2022/paper.tex
comparison with the earlier (2018) paper

Indeed, the consideration of \emph{all} battles allowed us to
consider battles where the hydra can make an arbitrary number of copies at any time, which make easier our proof by absurd.
Unfortunately, the examples  most shown in the litterature
(see for instance \cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof:

>>>>

Indeed, the consideration of \emph{all} battles allowed us to
consider battles where the hydra can make an arbitrary number of copies at any time, which make easier our proof by absurd.
Unfortunately, the examples  most shown in the litterature
(see for instance \cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.
